\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-27 document/XSGRB_sample.tex
GRB100901A

>>>>

	\subsection{GRB100901A(z=1.408)}
	The data presented here has been published in \citet{Hartoog2013}. Because of
	the unusual lingering brightness of this GRB, 2.4s of observations taken 65.98
	hours after the GRB trigger still reveals an afterglow continuum visible across
	the entire spectral coverage of X-shooter. Absorption lines from a wide range
	ion put the redshift at $z=1.408$, with intervening absorption systems at $z =
	1.3147$ and $z = 1.3179$.
